Structured Versus Decorated Cospans

### 2020-12-30 cospans.tex
dealt with "strict preservation of finite colimits" in Cor. 3.5 and start of proof of Thm. 3.2

%%% Combining \cref{lem:MonGroth,lem:fibrewiselimits}, we obtain the following corollary that sets up the statement of \cref{thm:equiv}.

\begin{cor}\label{cor:fcocMonGroth}
 Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor. If the corresponding pseudofunctor $F  \maps \A \to \SMC$ from \cref{lem:MonGroth} factors through $\Rex$, then $\inta F$ has all finite colimits 
 %%% which can be chosen in a way that the induced opfibration strictly preserves them.
 and the induced opfibration $U\maps \inta F \to \A$ preserves them.
\end{cor}

@@

By \cref{cor:fcocMonGroth}, since the corresponding pseudofunctor $F\maps\A\to\SMC$ factors through $\Rex$, the Gro\-the\-ndieck construction gives rise to a category $\inta F$ with finite colimits such that the corresponding opfibration $U\maps\inta{F}\to\A$ preserves them.  Using \cref{lem:fibrewiselimits} we choose finite colimits in $\inta{F}$ such that
$U$ strictly preserves these chosen colimits (which were already chosen in $A$).  
%%% By \cref{cor:fcocMonGroth}, since the corresponding pseudofunctor $F\maps\A\to\SMC$ factors through $\Rex$, the Gro\-the\-ndieck construction gives rise to a category $\inta F$ where we can choose finite colimits in a way that the corresponding opfibration $U\maps\inta{F}\to\A$ strictly preserves them.

@@

\begin{defn}
\label{defn:monoidal_double_category}
A \define{monoidal double category} is a pseudomonoid in $\Dbl$. 
\end{defn} 
\noindent
Explicitly, a monoidal double category is a double category $\lD$ with:
\begin{itemize}
\item monoidal structures on both $\lD_0$ and $\lD_1$ (each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$), such that $U \maps \lD_0 \to \lD_1$ strictly preserves the unit object and $S,T \maps \lD_1 \to \lD_0$ are strict monoidal,    %%% got rid of footnote saying that "isomorphic is okay" - jb %%% Great.
\item the structure of a double functor on $\otimes$:
that is, invertible globular 2-morphisms
\[ \chi \maps (M_2\otimes N_2)\odot(M_1\otimes N_1)  \simrightarrow
(M_2\odot M_1)\otimes (N_2\odot N_1)\]
\[ \mu \maps U_{A\otimes B} \simrightarrow U_A \otimes U_B\]
obeying a list of equations that can be found after \cite[Definition 2.10]{HS} and also \cite[Definition A.5]{BC}.
\end{itemize}

>>>>

\begin{cor}\label{cor:fcocMonGroth}
 Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor for which the corresponding pseudofunctor $F  \maps \A \to \SMC$ from \cref{lem:MonGroth} factors through $\Rex$.  Then $\inta F$ has all finite colimits and  the induced opfibration $U\maps \inta F \to \A$ preserves them.  Moreover we can choose finite colimits in $\inta F$ so that $U$ preserves them strictly.
\end{cor}

@@

Since the corresponding pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$, 
the Gro\-the\-ndieck construction gives rise to a category $\inta F$ with finite colimits, and 
we can choose these in such a way that the corresponding opfibration $U \maps \inta F \to \A$ strictly preserves them.  We do this in what follows.

@@

\begin{defn}
\label{defn:monoidal_double_category}
A \define{monoidal double category} is a pseudomonoid in $\Dbl$. 
\end{defn} 
\noindent
Explicitly, a monoidal double category is a double category $\lD$ with:
\begin{itemize}
\item monoidal structures on both $\lD_0$ and $\lD_1$ (each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$), such that $U \maps \lD_0 \to \lD_1$ strictly preserves the unit object and $S,T \maps \lD_1 \to \lD_0$ are strict monoidal,    
\item the structure of a double functor on $\otimes$:
that is, invertible globular 2-morphisms
\[ \chi \maps (M_2\otimes N_2)\odot(M_1\otimes N_1)  \simrightarrow
(M_2\odot M_1)\otimes (N_2\odot N_1)\]
\[ \mu \maps U_{A\otimes B} \simrightarrow U_A \otimes U_B\]
obeying a list of equations that can be found after \cite[Definition 2.10]{HS} and also \cite[Definition A.5]{BC}.
\end{itemize}
